---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

I added two new functions and three tests for each function in the package.


You can install the package by 

'install_github("liangqianSheng/foofactors")
library(foofactors)'


You can use the fbind() function to bind two factors together.


You can use the freq_out() funtion to create a data frame consisting of the levels of the factor and their frequency.


You can use the cuttable(x,a) function to cut a numeric factor "x" into "a" intervals and make a distribution table for the factor.


You can use the addPercent() function to add "%" to the factor.


```{r}
#install_github("liangqianSheng/foofactors")
library(foofactors)
fbind(iris$Species[c(1, 51, 101)], PlantGrowth$group[c(1, 11, 21)])
freq_out(iris$Species)
cuttable(iris$Sepal.Width,3)
addPercent(iris$Sepal.Length)
```



